---
output:
  pdf_document: default
  html_document: default
---
# Statistical Inference Project Part 2 - Basic Inferential Data Analysis On ToothGrowth

loading library
```{r}
library(ggplot2)
library(datasets)
data(ToothGrowth)
str(ToothGrowth)
summary(ToothGrowth)
```

Plotting length vs dose boxplots for different supp

```{r}
ggplot(data = ToothGrowth , aes(x = as.factor(dose),y = len)) + geom_boxplot(aes(fill= dose)) + facet_grid(.~supp)
```


length vs supplementary

```{r}
ggplot(data = ToothGrowth , aes(x = as.factor(supp),y = len)) + geom_boxplot(aes(fill= supp)) + facet_grid(.~dose)
```

###T test to compare length for different supplements
```{r}
t.test(len~supp,data = ToothGrowth)
```

Since the p value is greater then 0.05 , we can say that the null hypothesis is true

###t test to compare length for different doses

comparing 1.0 and 2.0

```{r}
subsett <- ToothGrowth[ToothGrowth$dose %in% c(1.0,2.0),]
t.test(len~as.factor(dose),data = subsett)
```

comparing 1.0 and 0.5

```{r}
subsett <- ToothGrowth[ToothGrowth$dose %in% c(1.0,0.5),]
t.test(len~as.factor(dose),data = subsett)
```
comparing 2.0 and 0.5

```{r}
subsett <- ToothGrowth[ToothGrowth$dose %in% c(2.0,0.5),]
t.test(len~as.factor(dose),data = subsett)
```

for all the cases the p values is nearly zero . Therefore the null hypothesis can be rejected . 
Hence tooth length increases with an increase in the dose