---
output:
  pdf_document: default
  html_document: default
---
# Statistical Inference Project 

## Overview
This project investigates the Exponential distribution in R and compares it with the Central Limit Theorem. The mean of the Exponential distribution is $\frac{1}{\lambda}$ and the standard deviation is also $\frac{1}{\lambda}$. A thousand simulations of the distribution of 40 exponentials would be investigated.

## Simulation
The exponential distribution can be simulated in R with rexp(n, lambda), where lambda is the rate parameter and n is the number of observations. For the purpose of all the simulations in this project, value of lambda is set to 0.2.
First we load the ggplot2 plotting library.

```{r}
library(ggplot2)
```

Then we will initialize the variables

```{r}
lamb <- 0.2
n <- 1000
sampsize <- 40
```

set seed for random variable

```{r}
set.seed(3)
```

create a matrix with 1000 rows and 40 column

```{r}
sampledMatrix <- matrix(rexp(sampsize*n , lamb) ,n, sampsize)
```

We find the means for each simulation

```{r}
means <- apply(sampledMatrix,1,mean)
```


calculate the simulated data

```{r}
sampleData <- data.frame(cbind(sampledMatrix,means))
```

plot the simulated means data

```{r}
ggplot(data = sampleData , aes(means)) + geom_histogram(aes(fill=..count..) , bins = round(sqrt(1000),1)) + geom_vline(xintercept = mean(means))
```

```{r}
actualMean <- mean(sampleData$means)
theoreticalMean <- 1/lamb
```

The Actual Mean is `r actualMean`

The Theoretical Mean is `r theoreticalMean`

```{r}
ggplot(data = sampleData , aes(means)) + geom_histogram(aes(y = ..density.. ,fill=..count.. , bins = sqrt(length(means)))) + geom_density(aes(y=..density.., colour='Empirical'), size=1)
```

as we see it is nearly normal

```{r}
actualVariance <- var(means)
theoreticalVariance <-( (1/lamb)^2)/40
```

the actual Variance is `r actualVariance`

the theoretical Variance is `r theoreticalVariance`

```{r}
actualConf <- actualMean +c(-1,1)*qnorm(0.95)*sqrt(actualVariance)
theoreticalConf <- theoreticalMean + c(-1,1)*qnorm(0.95)*sqrt(theoreticalVariance)
```


the actual 95% Conf is `r actualConf` and the theoretical conf is `r theoreticalConf` 
